Growing libraries of concepts with wake-sleep program induction

### 2018-07-21 talk.tex
small edits to slides

\end{frame}
\begin{frame}[t]{Sleep-R: Experience replay}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}
\end{frame}
\begin{frame}[t]{Sleep-R: Dreaming}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}

>>>>

\end{frame}
\begin{frame}[t]{Sleep-R: Objective}
  \includegraphics[width = 11cm]{figures/animation/Wake.eps}

    \vfill
    Recognition model predicts distribution over program, conditional on task.\\
    Training: (program, task) pairs\\
    Objective: Predict program w/ (1) high prior under DSL \& \\(2) high likelihood for task

\end{frame}
\begin{frame}[t]{Sleep-R: Experience replay}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}

    \textbf{Train on (program, task) pairs found during waking}
\end{frame}
\begin{frame}[t]{Sleep-R: Dreaming}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}

    \textbf{Train on (program, task) pairs sampled from DSL}
